---
title: "Steven Universe"
output: html_notebook
---
# Worcester Election Data

This project uses data from [City of Worcester Open] (https://gisdata.worcesterma.gov/)
## Let's make a new section here with a level 1 header labeled something like "Worcester Election Data"
- use rmarkdown to create the section header 
- use rmarkdown to make a link that indicates where we got the data: https://gisdata.worcesterma.gov/
- use plain text to write that this section will show us where Worcester precincts and voting locations are.
```{r}
```

```{r}
library(sf) #here we tell R that we need the Simple Features library (sf)
library(tmap)    # for static and interactive maps
library(leaflet) # for interactive maps
library(ggplot2) # tidyverse data visualization package

#then we create an object called "precs," which is short for precincts and fill it with the data from our geojson file
precs = read_sf("data/Voting_Precincts_Based_on_2020_Census_Data.geojson")

#the "head" function tells us what is in the object and what kind of object it is
head(precs)

#let's plot our object
tm_shape(precs) + 
  tm_fill()

#now let's try it with some borders
tm_shape(precs) + 
  tm_fill(col="coral") +
  tm_borders(col="white")

#what about some labels?
tm_shape(precs) + 
  tm_fill(col="violetred3")+
  tm_borders(col="white") +
```
```{r}
```

```{r}
tm_text("Ward_Precinct" , size = "AREA", col="blue")

#that didn't work? how do we learn more about our tm_* (tmap) functions?
?tmap

#R will let you make a map object and reuse it
woo_map1 = tm_shape(precs)+tm_fill(col="blue")+tm_borders(col="yellow")

```

# Polling Stations 
Your task is to make a new section that imports the voting polling stations and places them on a map.
```{r}
polls=read_sf("data/Polling_Locations.geojson")
woo_map2 = tm_shape(polls) + tm_symbols()
woo_map1+woo_map2
```

